Peaks Over Threshold for Bursty Time Series

### 2018-04-18 article_springer/article_springer.Rmd
add threshold selection literature

Conditional on the last threshold being

```{r hazard, fig.height=7, fig.cap="Left: Conditional distribution of time until next threshold crossing, depending on elapsed time since last crossing ($\\beta = 0.8$, $\\sigma_0 = 1$). Right: Hazard rate depending on tail parameter $\\beta$.\\label{fig:hazard}"}
tail <- 0.7
scale <- 1
t_0 <- c(0, 1, 10)
from <- 0.1
to <- 100 * scale
xx <- exp(seq(from = log(from), to = log(to), length.out = 100))
par(mfrow = c(2,2))
plot(xx, rep(1, length(xx)), ylim = c(0.001,1), type = 'n', log = 'xy', 
     xlab = 't', ylab = 'p')
for (k in 1:length(t_0)) {
  cond <- pml(q = t_0[k], tail = tail, scale = scale, lower.tail = FALSE)
  yy <- dml(x = xx + t_0[k], tail = tail, scale = scale) / cond
  lines(xx,yy, col = k+1, lty = k)
}
legend("bottomleft", c("t_0 = 0", "t_0 = 1", "t_0 = 10"), col = 2:4, lty = 1:3)

@@

>>>>

```{r hazard, fig.height=7, fig.cap="Left: Conditional distribution of time until next threshold crossing, depending on elapsed time $t_0$ since last crossing ($\\beta = 0.8$, $\\sigma_0 = 1$). Right: Hazard rate depending on tail parameter $\\beta$.\\label{fig:hazard}"}
tail <- 0.7
scale <- 1
t_0 <- c(0, 1, 10)
from <- 0.1
to <- 100 * scale
xx <- exp(seq(from = log(from), to = log(to), length.out = 100))
par(mfrow = c(2,2))
plot(xx, rep(1, length(xx)), ylim = c(0.001,1), type = 'n', log = 'xy', 
     xlab = 't', ylab = 'p')
for (k in 1:length(t_0)) {
  cond <- pml(q = t_0[k], tail = tail, scale = scale, lower.tail = FALSE)
  yy <- dml(x = xx + t_0[k], tail = tail, scale = scale) / cond
  lines(xx,yy, col = k+1, lty = k)
}
legend("bottomleft", c("t_0 = 0", "t_0 = 1", "t_0 = 10"), col = 2:4, lty = 1:3)

@@

It is beyond the scope of the current paper to incorporate parameter 
uncertainty into our predictive distribution for the next threshold crossing; 
however, methods as described by @Scarrott12 and @Lee15 are likely 
to extend to our setting.
